Pillar 2 - Topic Modeling

### 2019-01-23 Pillar 2 - Topic Modeling.Rmd

```{r LDA fit, cache = TRUE}
n_topics <- 120
levels   <- c("description", "overview", "manual")
list_nam <- character(0)

@@

  dataset   <- get(paste("d", level, "cast", sep = "_"))
  LDA_model <- LDA(dataset, k = n_topics, control = list(seed = 123))
  nam <- paste("LDA", level, n_topics, sep = "_")

@@

### Plots
```{r LDA plot, cache = TRUE}
LDA_description_120 %>% visualize_LDA_all_level(id_plot = "description_k120")

LDA_overview_120 %>% visualize_LDA_all_level(id_plot = "overview_k120")

LDA_manual_120 %>% visualize_LDA_all_level(id_plot = "manual_k120")
```

>>>>

```{r LDA fit, cache = TRUE}
n_topics <- 5
levels   <- c("description", "overview", "manual")
list_nam <- character(0)

@@

  dataset   <- get(paste("d", level, "cast", sep = "_"))
  LDA_model <- LDA(
    x = dataset,
    k = n_topics,
    method = "Gibbs",
    control = list(
      nstart = 10,
      seed = c(1:10),
      best = TRUE,
      burnin = 4000,
      iter = 2000,
      thin = 500))
  nam <- paste("LDA", level, n_topics, sep = "_")

@@

### Plots
```{r LDA plot, cache = TRUE}
load("LDA.RDATA")

LDA_description_5 %>% visualize_LDA_all_level(id_plot = "description_k5")

LDA_overview_5 %>% visualize_LDA_all_level(id_plot = "overview_k5")

LDA_manual_5 %>% visualize_LDA_all_level(id_plot = "manual_k5")
```
